Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-03 method.tex
Fleshed out caption
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@930 ccdd05d5-56c1-461a-bf98-85f6876523b4

\Table{\label{table:flops}Minimum computational cost of the \fir{} filter bank, \fft{} convolution, and \lloid\ methods for a bank of 657 templates sampled at 4096 Hz.}
\br
Method & \flops \\
\mr
\fir{} & $2.4\times10^{13}$ \\
\fft{} convolution & $2.6\times10^8$ \\
\lloid & $4.7\times10^8$ \\
\br
\end{tabular}
\end{indented}
\end{table}

>>>>

\Table{\label{table:flops}Computational cost in \flops\ of the \TD\ method, the \FD\ method, and \lloid\ for the bank of $2 \times 657$ templates sampled at 4096 Hz for chirp masses $1.955 \leqslant \mathcal{M} / M_\odot \leqslant 1.2045$.  A block size of $D = 2 N$ is used for the \fft{}s in the \FD\ method.}
\br
Method & \flops \\
\mr
\fir{} & $2.4\times10^{13}$ \\
\fft{} convolution & $2.6\times10^8$ \\
\lloid & $4.7\times10^8$ \\
\br
\end{tabular}
\end{indented}
\end{table}
